Races with hyper3 objects

### 2024-03-04 inst/race3.Rmd

Looking at the first column we see that the constructors are Mercedes
("`Merc`"), Red Bull Racing Honda ("`RBRH`"), and so on (see file
`inst/constructor_names.txt` for a list of abbreviations).  Each
constructor fields two cars in each race.  Looking at the next column,
we see the order statistic for Bahrain (`BHR`).  We see that Mercedes
came first and third, Red Bull came second and fifth, Ferrari sixth
and eighth, and so on.

@@

and see that there is (very) strong evidence to reject this null.
Further, we may test the hypothesis that the big four (viz Mercedes,
Ferrari, Red Bull Racing Honda, and McLaren-Mercedes) are equal:

```{r,label=testsameconstructor,cache=TRUE}
samep.test(constructor_2021,c("Merc","Ferrari","RBRH","MM")) # ~10 mins
```

@@

```{r,label=testsameconstructorlowscores,cache=TRUE}
samep.test(constructor_2021,c("ATH","ARRF","AR","AMM")) # ~ 10 mins
```

@@

```{r,label=changenames,cache=TRUE}
constructor_2020_and_2021 <- psubs(constructor_2020,"Merc","Merc2020") + psubs(constructor_2021,"Merc","Merc2021")
```

>>>>

Looking at the first column we see that the constructors are Mercedes
RedBull, and so on (file `inst/constructor_names.txt` summarises the
constructors' lifespans).  Each constructor fields two cars in each
race.  Looking at the next column, we see the order statistic for
Bahrain (`BHR`).  We see that Mercedes came first and third, RedBull
came second and fifth, Ferrari sixth and eighth, and so on.

@@

and see that there is (very) strong evidence to reject this null.
Further, we may test the hypothesis that the big four (viz Mercedes,
Ferrari, RedBull, and McLaren) are equal:

```{r,label=testsameconstructor,cache=TRUE}
samep.test(constructor_2021,c("Mercedes","Ferrari","RedBull","McLaren")) # ~10 mins
```

@@

```{r,label=testsameconstructorlowscores,cache=TRUE}
samep.test(constructor_2021,c("Alpine","AlphaTauri","AstonMartin")) # ~ 10 mins
```

@@

```{r,label=changenames,cache=FALSE}
constructor_2020_and_2021 <- psubs(constructor_2020,"Mercedes","Merc2020") + psubs(constructor_2021,"Mercedes","Merc2021")
```
